% Thesis Acknowledgements ----------------------------------------------
\prefacesection{Acknowledgements}


First, I would like to thank my advisor, Justin Cappos, for his guidance throughout this program.  I would not have been able to complete this effort without his uncanny ability to find and guide me down the best path, no matter what I came up against.
Next, I would like to thank my co-advisor, Phyllis Frankl, for her support and encouragement. She was a great resource for both how to navigate through the program, and for practical advice on teaching large, intimidating classes.
Also thank you to Brendan Dolan-Gavitt for helping define my research direction all those long years ago.
Further, I would like to thank Thomas Wies and Marc Waldman for their enormous assistance.  I was often out of my depth and appreciate you helping me stay afloat.
Finally, nothing I built or wrote would have made it out of the lab without Lois DeLong.  Thank you for giving me writing skills that will benefit me for the rest of my life.

Throughout this program I received a great deal of much appreciated support and encouragement from my lab-mates: Marina Moore, Aditya Sirish Yelgundhalli, Nick Renner, Santiago Torres Arias, Yiwen Li, and Trishank Kuppusamy. It has been a blast working with you all.
I also need to thank my support team outside the lab: Brian Neel, Evan Arthur, Robin Zapata, Vincent Benavides and the rest of my New York Family. You have my gratitude for enduring countless stress-induced rants about whatever was going wrong at any given point in time.

I cannot end these acknowledgements without mentioning my parents, Rick and Stephanie, and my brother Alex.  Thank you for providing the encouragement and reassurance I needed to take on an intimidating goal far from home.  Finally, I would not be the person I am today without my partner, Morgan Lamb.  Thank you for always being there for me!

\bigskip\medskip

\noindent \hfill Preston Moore, New York University Tandon School of Engineering

\hfill \today

% ----------------------------------------------------------------------
